\MakeUppercase{Graph Product Structure for Non-Minor-Closed Classes}

### 2022-04-05 response.tex

  The notations $Y_x$ and $B_x$ are needed since we need names for the parts of the $H$-decomposition of $G$ and the bags in the tree-decomposition of $H$.    The notation $C_x$ is limited to the proof of (newly-numbered) Claim~3, where it is used to denote the bags in the tree-decomposition that is the subject of Claim~3.

  We have avoided the introduction of any new notation, including $\phi$.  The new presentation is much shorter and clearer.  We thank the referee for making us revisit this proof carefully.  The final paper is better for it.
\end{response}

3. Theorem 10: Unfortunately I have to suggest removing it. I don’t see
the motivation for making $H$ planar or for improving the constants.
Are the improved constants at all close to tight? Is there another
reason for including it?

\begin{response}
There is a lot of motivation for proving this result with $H$ of treewidth 3 and planar. First, the treewidth bound is best possible (even for planar graphs). Having $H$ planar means that $H$ is in fact a planar 3-tree (also called stack polytope or Appolonian network). It follows that we get better bounds for queue-number for example.

@@

4. page 6, line 14: ``Thus, it suffices to construct width-$t$ tree decomposition that satisfies (T2).'' $\longrightarrow$ should be (T1)

\done

5. page 6, line 16: ``Select any node $x \in V (T_0)$'' $\longrightarrow$ ``Select any nonempty node $x \in V (T_0)$''

\textcolor{blue}{All the bags at this point are non-empty. We have revised to make this clear. }

@@

Page 13. The attached PDF also shows that the definition of 'kite
face' may not be well-defined.  For example, I do not see why there
cannot be some edges of $G$ 'inside' a kite face.  Even if this is not
the case, I think it is more precise to say that a kite face has 'two
and a half edges' and two vertices of $G$ on its boundary' rather than
'three edges and two vertices of $G$ on its boundary'.

\textcolor{blue}{Our definition of kite was not exactly what we meant. This section has been completely revised.}

Page 13.  Regarding the proof of Lemma 4, I think it is better to
include all the details from reference [14].  As far as I know, JCTB
does not have a page limit, so I do not see an issue with just
reproducing the entire proof and telling the reader that they can skip
all the details if they wish.  This is just my personal opinion
though, so the authors can ignore this request if they choose.

\textcolor{blue}{Upon reflection we agree with the referee here. Indeed, while cleaning up this proof we have also improved the constant from $30$ to $7$. The proof is similar to the previous proof except that graph $G'$ is obtained by removing both crossing edges involved in a crossing (the spars of a kite), rather than just one.  We now use the language of framed multigraph, for consistency with the literature. Thanks to the referee for forcing us to write this proof more carefully so that we could discover this improvement.}

@@

Page 18. In point 1 in the proof of Lemma 9, I think '$\phi(w)$' should
be '$\alpha(w)$'.

\changed

Page 18.  Say $H'$ is connected since $X$ is connected.

\textcolor{blue}{This proof is now removed since the authors of [10] included this result in the journal version of their paper.}

### 2022-04-05 k-planar.tex
added some suggestions, updated response

\note{DW}{I'm not comfortable about saying that $k$-planar graphs are our most high-profile target. Why are they more important than map graphs, say?}

>>>>

\note{DW}{I'm uncomfortable about saying that $k$-planar graphs are our most high-profile target. Why are they more important than map graphs or nearest neighbour graphs? I suggest ``
The above result for $k$-planar graphs (\cref{kPlanarProduct}) is in fact a special case of a more general result that relies on the following definition. A non-empty set $\SS$  ....''}
